R für die sozio-ökonomische Forschung

### 2020-01-12 Chap-data.Rmd

#  Datenkunde und Datenaufbereitung {#data}

```{r include=FALSE}
knitr::opts_chunk$set(comment = "#>")
```

@@

```{r, echo=FALSE, fig.align='center'}
knitr::include_graphics("figures/chap-data-Ablaufschema.png")
```

@@

```{r}
data_bip_gini_left_join <- inner_join(data_BIP, data_gini, 
                                      by=c("Jahr"="year", "Land"="country"))
data_bip_gini_left_join
```

>>>>

---
output:
  pdf_document: default
  html_document: default
---
#  Datenkunde und Datenaufbereitung {#data}

```{r include=FALSE}
knitr::opts_chunk$set(comment = "#>")
knitr::opts_chunk$set(out.height = '75%', out.width = '75%', fig.align = 'center') 
```

@@

```{r, echo=FALSE, fig.align='center'}
knitr::include_graphics("figures/chap-data-Ablaufschema.png", auto_pdf = T)
```

@@

```{r}
data_bip_gini_inner_join <- inner_join(data_BIP, data_gini, 
                                      by=c("Jahr"="year", "Land"="country"))
data_bip_gini_inner_join
```
